### 2023-03-14 main.tex
DualityCheckCheck
Update main.tex

\begingroup
% \centering
\begin{center}
 \begingroup\LARGE
\bf Stirring process
\par\endgroup
 \vspace{3.5em}
 \begingroup\large \bf
% {Rouven Frassek}
 \par\endgroup
\vspace{2em}

@@

Consider the $gl(N)$ Lie algebra with with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
\begin{equation}\label{eq:comgl}
\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{bc}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}
\end{equation}
The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu$. We assume $\lambda_i\geq \lambda_{i+1}$ without loss of generality.
We are interested in the {\em symmetric} finite-dimensional representations with 
\begin{equation}\label{eq:dynkin}
    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}
\end{equation} 
The dimension $M$ of the symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition, namely
\begin{equation}
	M= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
\end{equation} 
The basis elements of the vector space $\mathbb{C}^{M}$ are the column vectors 
\begin{equation}
  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{sucht that}\quad \sum_{i=1}^{N}n_{i}=\nu
\end{equation}
%where $\sum_{k=1}^{N}n_{i}=\nu$. 
This basis vector satisfy the orthogonality relation with respect to the Euclidean scalar product 
\begin{equation}\label{ortho}
    \langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{k=1}^{N}\delta_{m_{k},n_{k}}
\end{equation}
where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{m_{k},n_{k}}$ is the Kronhecker delta. 
The explicit actions of the algebra generators on the vectors $|n\rangle$ are the following:
\begin{equation}\label{actionE}
	\begin{cases}
		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle\quad a=b
	\end{cases}
\end{equation}  
One can check that the matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}.

@@

%We now define the equivalent of \eqref{stateSpace} in the vector notation
% \begin{equation}
%	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
%	\end{equation}
%where we denote 
\begin{equation}
|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1}^{x},\ldots,n_{N}^{x}\rangle\right)
\end{equation}
where we require that $n_{k}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{k=1}^{N}n_{k}^{x}=\nu$. The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
\begin{equation}
    \langle {\bf n}|{\bf m}\rangle =\prod_{x=1}^L\prod_{i=1}^N\delta_{n^x_i,m^{x}_i}
\end{equation}
We introduce the Hamiltonian operator

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
H_{x,y}=\sum_{k,\ell=1}^{N}\left(E_{k\ell}^{x}\otimes E_{\ell k}^{y}-E_{\ell\ell}^{x}\otimes E_{kk}^{y}\right)
 \end{equation}
 {\color{red}confusing notation: tensor product and site index.... Remove tensor product?}

 and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{k,\ell=1}^{N}\alpha_{k}^{x}\left(E_{k\ell}^{x}-E_{\ell\ell}^{x}\right)
\end{equation}
Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$. 
Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
\begin{equation}
H=\mathcal{L}^{T}
\end{equation}
The generator can also be expressed as

\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {\bf n\in \Omega}}f( {\bf n})\langle  {\bf n}|
\end{equation}

We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir of $gl(N)$
\begin{equation}\label{secondCasimir}
    C_{2}=\sum_{a,b=1}^{N}E_{ab}E_{ba}
\end{equation}
that acts diagonally as $C_{2}|\mathbf{n}\rangle=\twoj(\twoj+N)|\mathbf{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the basis elements).  \\
 Considering two sites $x,y\in \mathcal{E}$ the standard coproduct operator is defined as 
\begin{equation}
\begin{split}
\Delta^{x,y}:gl(N)&\to gl(N)\otimes gl(N)\\
E_{ab}&\to E_{ab}^{x}\otimes \mathbbm{1}^{y}+\mathbbm{1}^{x}\otimes E_{ab}^{y}
\end{split}
\end{equation}
therefore, we have 
\begin{equation}
\Delta^{x,y}(C_{2})=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}^{x}\otimes E_{ba}^{y}+C_{2}^{x}\otimes \mathbbm{1}^{y}+\mathbbm{1}^{x}\otimes C_{2}^{y}
\end{equation}

One can check that 
\begin{equation}\label{hamiltonianCasimir}
	H_{x,y}=\frac{1}{2}\Delta^{xy}(C_{2})-\twoj(2\twoj+N)\mathbbm{1}^{x}\otimes\mathbbm{1}^{y}
\end{equation}

@@

\section{Duality}
\subsection{Definition of duality}
Consider two Markov processes: $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$. We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$, if $\forall \eta\in\Omega$, $\forall \xi\in\widetilde{\Omega}$ and $\forall t> 0$ we have 
\begin{equation}
    \mathbb{E}_{\eta}\left[D(\eta_{t},\xi)\right]=\mathbb{E}_{\xi}\left[D(\eta,\xi_{t})\right]
\end{equation}
where $\mathbb{E}_{\eta}$ denotes the expectation with respect the law of the Markov process $(\eta_{t})_{t\geq 0}$ initialized with the particle configuration $\eta$, whereas $\mathbb{E}_{\xi}$ denotes the expectation with respect the law of the Markov process $(\xi_{t})_{t\geq 0}$ initialized with the particle configuration $\xi$.
The duality definition can also be formulated as a relation between the generators. Call $\mathcal{L}$ the generator of $(\eta_{t})_{t\geq0}$ and $\widetilde{\mathcal{L}}$ the generator of $(\xi_{t})_{t\geq 0}$, then we say that these two processes are dual with respect the duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$ if $\forall \eta\in\Omega$ and $\forall \xi\in\widetilde{\Omega}$ if
\begin{equation}\label{dualityRelationGenerator}
    \left(\mathcal{L}D(\cdot,\xi)\right)(\eta)=\left(\widetilde{\mathcal{L}}D(\eta,\cdot)\right)(\xi)
\end{equation}
\textbf{Remark}:
in the specific case where $\mathcal{L}=\widetilde{\mathcal{L}}$ we say that the processes are self-dual with respect to a self-duality function.
\newline
\newline
\textbf{Remark}:
when the state spaces of the dual processes is finite, the generators and the duality function are matrices with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$. Therefore, we can write the duality relation \eqref{dualityRelationGenerator} as 
\begin{equation}
    \sum_{\eta^{'}\in\,\Omega}\mathcal{L}(\eta,\eta^{'})D(\eta^{'},\xi)=\sum_{\xi^{'}\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi^{'})D(\eta,\xi^{'})
\end{equation}
that can be read as
\begin{equation}\label{dualityIntertwines}
    \mathcal{L}D=D\widetilde{\mathcal{L}}^{T}
\end{equation}
where the superscript $T$ denotes the matrix transposition. Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining transformation between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}$. Working with the Hamiltonian operators the duality relation \eqref{dualityIntertwines} reads as
\begin{equation}\label{DualityRelation}
    H^{T}D=D\widetilde{H}
\end{equation}
where $\widetilde{H}=\widetilde{\mathcal{L}}^{T}$.
\subsection{Duality for the generalized multi-species boundary driven stirring process}
We now state our duality result. The process $|\mathbf{n}\rangle$ with Hamiltonian \eqref{OriginalHamiltonian} is dual in the sense of \eqref{DualityRelation}, with respect to a process $|\bm{\xi}\rangle$ defined on the enlarged state space
\begin{equation}
    \widetilde{\Omega}:=\Omega\times \mathbb{N}_{0}^{V}
\end{equation}
with elements
\begin{equation}
    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|r_{1}^{x},\ldots,r_{N}^{x}\rangle\otimes |m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}\rangle\right)
\end{equation}
where $r_{x}^{k}$ denotes the number of dual particles of type $k\in \{1,\ldots,N\}$ at site $x\in V$ and $m_{k}^{\widetilde{x}}$ denotes the number of particles of species $k\in \{2,\ldots,N\}$ at an extra-site $\widetilde{x}$ connected to the site $x\in V$.\\
The Hamiltonian of the dual process reads as
\begin{equation}\label{DualHamiltonian}
    \widetilde{H}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{H}_{x}
\end{equation}

where $H_{x,y}$ is the one defined in \eqref{edgeHamiltonian}, while 
\begin{equation}\label{siteDualHamiltonian}
    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left((a^{\dagger})_{k}^{\widetilde{x}}\,E_{1k}^{x}-E_{kk}^{x}\right)
\end{equation}
By introducing the action of a bosonic creation operator $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, we define in \eqref{siteDualHamiltonian} 
$(a^{\dagger})_{k}^{\widetilde{x}}$ as a copy of $a^{\dagger}$ acting on the extra-site $\widetilde{x}$ and on the occupation of the species $k\in\{2,\ldots,N\}$. \\
The Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual with respect to the duality matrix $D$ defined as 
\begin{equation}
    D=\bigotimes_{x\in V}\left(D_{x}\otimes D_{\widetilde{x}}\right)
\end{equation}
We denote by $D_{x}$ the site part. This is defined as 
\begin{equation}
    D_{x}=R_{x}\exp{(E^{x})}
\end{equation}
with 
\begin{equation}
    E^{x}=\sum_{k=2}^{N}E_{k1}^{x}
\end{equation}
that implies 
\begin{equation}
    \exp{(E^{x})}=I+E^{x}
\end{equation}
and where $R_{x}$ is the diagonal matrix with elements (up to a finite constant) the inverse of the masses of the reversible measure \eqref{reversibleMeasure}, i.e. 
\begin{equation}
    R_{x}=\sum_{n\in\chi}\frac{\prod_{k=1}^{N}n_{k}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
\end{equation}
where, for all $x\in V$, we call $\chi=\{(n_{k}^{x})_{k\in\{1,\ldots,N\}}\in \mathbb{N}_{0}\,:\, \sum_{k=1}^{N}n_{k}^{x}=\nu\}$ the simplex.\\ 
We denote by $D_{\widetilde{x}}$ the extra-site part. It is defined as
\begin{equation}\label{dualityMatrix}
D_{\widetilde{x}}=\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
\end{equation}
On one hand, the edge part of the dual Hamiltonian \eqref{DualHamiltonian} is a copy of \eqref{edgeHamiltonian}, therefore it performs the stirring dynamic on the graph. On the other hand, the site dual Hamiltonian \eqref{siteDualHamiltonian} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widetilde{x}$. This means that, eventually, only particles of type $1$ remain in the graph while all other types are absorbed by the extra-sites. Thinking about the type $1$ as the hole  the graph is eventually emptied, similarly to what proved in the SEP(2j)\cite{carinci2013duality}.
\subsection{Proof of the duality relation}\label{subsectionDualityProof}
To prove the duality relation between \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} with the duality matrix \eqref{dualityMatrix} we shall show that 
\begin{equation}
    H^{T}D=D\widetilde{H}
\end{equation}
Since the duality matrix is a tensor product over the sites $x\in V$ it is enough to prove that for the edge Hamiltonians
\begin{equation}\label{edgeDualRealtion}
    H_{x,y}^{T}D=DH_{x,y}\qquad \forall x,y\in \mathcal{E}
\end{equation}
and for the site Hamiltonians 
\begin{equation}\label{siteDualRelation}
    H_{x}^{T}D=D\widetilde{H}_{x}\qquad \forall x\in V.
\end{equation}
We will prove these two statements seprately in the following.

@@

>>>>

\begingroup
% \centering
\begin{center}
 \begingroup\LARGE
\bf Multispecies stirring process
\par\endgroup
 \vspace{3.5em}
 \begingroup\large \bf
% {Rouven Frassek}
 \par\endgroup
\vspace{2em}

@@

Consider the Lie algebra $gl(N)$ with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
\begin{equation}\label{eq:comgl}
\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{bc}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}
\end{equation}
The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu$. We assume $\lambda_i\geq \lambda_{i+1}$ without loss of generality.
We are interested in the {\em symmetric} finite-dimensional representations with 
\begin{equation}\label{eq:dynkin}
    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}
\end{equation} 
The dimension $M$ of the symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition, namely
\begin{equation}
	M= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
\end{equation} 
The basis elements of the vector space $\mathbb{C}^{M}$ are the column vectors 
\begin{equation}
  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{sucht that}\quad \sum_{i=1}^{N}n_{i}=\nu
\end{equation}
%where $\sum_{k=1}^{N}n_{i}=\nu$. 
This basis vector satisfy the orthogonality relation with respect to the Euclidean scalar product 
\begin{equation}\label{ortho}
    \langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{k=1}^{N}\delta_{m_{k},n_{k}}
\end{equation}
where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{m_{k},n_{k}}$ is the Kronhecker delta. 
The explicit actions of the algebra generators on the vectors $|n\rangle$ are the following:
\begin{equation}\label{actionE}
	\begin{cases}
		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle\quad a=b
	\end{cases}
\end{equation}  
One can check that the matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}.

@@

%We now define the equivalent of \eqref{stateSpace} in the vector notation
% \begin{equation}
%	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
%	\end{equation}
%where we denote 
\begin{equation}
|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1}^{x},\ldots,n_{N}^{x}\rangle\right)
\end{equation}
where we require that $n_{k}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{k=1}^{N}n_{k}^{x}=\nu$. The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
\begin{equation}
    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{i=1}^N\delta_{n^x_i,m^{x}_i}
\end{equation}
We introduce the Hamiltonian operator

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
H_{x,y}=\sum_{k,\ell=1}^{N}\Big(E_{k\ell}^{x} E_{\ell k}^{y}-E_{\ell\ell}^{x} E_{kk}^{y}\Big)
 \end{equation}
  and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{k,\ell=1}^{N}\alpha_{k}^{x}\left(E_{k\ell}^{x}-E_{\ell\ell}^{x}\right)
\end{equation}
Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$. 
Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
\begin{equation}
H=\mathcal{L}^{T}
\end{equation}
The action of the generator can also be expressed as 
\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {{\bf n}\in \Omega}}f( {\bf n})\langle  {\bf n}|
\end{equation}

We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir of $gl(N)$
\begin{equation}\label{secondCasimir}
    C_{2}=\sum_{a,b=1}^{N}E_{ab}E_{ba}
\end{equation}
that acts diagonally as $C_{2}|\mathbf{n}\rangle=\twoj(\twoj+N)|\mathbf{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the algebra elements).  
More precisely,  considering the standard coproduct 
\begin{equation}
\begin{split}
\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
\end{split}
\end{equation}
we have 
\begin{equation}
\Delta(C_{2})=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}\otimes E_{ba}+C_{2}\otimes \mathbbm{1}+\mathbbm{1}\otimes C_{2}
\end{equation}
Then, one can check that 
\begin{equation}\label{hamiltonianCasimir}
	H_{x,y}=\frac{1}{2}\Delta^{x,y}(C_{2})-\twoj(2\twoj+N)
\end{equation}
where $\Delta^{x,y}(C_2)$ denotes a copy of $\Delta(C_2)$ acting on  
the edge $(x,y)\in \mathcal{E}$.

@@

\section{Duality}
\subsection{Definition}
Consider two Markov processes $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$. We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$, if $\forall \eta\in\Omega$, $\forall \xi\in\widetilde{\Omega}$ and $\forall t> 0$ we have 
\begin{equation}
    \mathbb{E}_{\eta}\left[D(\eta_{t},\xi)\right]=\mathbb{E}_{\xi}\left[D(\eta,\xi_{t})\right]
\end{equation}
where $\mathbb{E}_{\eta}$ denotes the expectation with respect the law of the Markov process $(\eta_{t})_{t\geq 0}$ initialized with the particle configuration $\eta$, whereas $\mathbb{E}_{\xi}$ denotes the expectation with respect to the law of the Markov process $(\xi_{t})_{t\geq 0}$ initialized with the particle configuration $\xi$.
The duality definition can also be formulated as a relation between the generators. Call $\mathcal{L}$ the generator of $(\eta_{t})_{t\geq0}$ and $\widetilde{\mathcal{L}}$ the generator of $(\xi_{t})_{t\geq 0}$, then we say that these two processes are dual with respect to the duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$ if $\forall \eta\in\Omega$ and $\forall \xi\in\widetilde{\Omega}$
\begin{equation}\label{dualityRelationGenerator}
    \left(\mathcal{L}D(\cdot,\xi)\right)(\eta)=\left(\widetilde{\mathcal{L}}D(\eta,\cdot)\right)(\xi)
\end{equation}
In the specific case where $\mathcal{L}=\widetilde{\mathcal{L}}$ we say that the process is self-dual.
\newline
\newline
\textbf{Remark}:
when the state spaces of the dual processes is finite, the generators and the duality function are matrices with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$. Therefore, we can write the duality relation \eqref{dualityRelationGenerator} as 
\begin{equation}
    \sum_{\eta^{'}\in\,\Omega}\mathcal{L}(\eta,\eta^{'})D(\eta^{'},\xi)=\sum_{\xi^{'}\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi^{'})D(\eta,\xi^{'})
\end{equation}
that can be read as
\begin{equation}\label{dualityIntertwines}
    \mathcal{L}D=D\widetilde{\mathcal{L}}^{T}
\end{equation}
where the superscript $T$ denotes the matrix transposition. Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}$. Working with the Hamiltonian operators the duality relation \eqref{dualityIntertwines} reads 
\begin{equation}\label{DualityRelation}
    H^{T}D=D\widetilde{H}
\end{equation}
\subsection{Duality for the multi-species stirring process}
We now state our duality result. The process $|\mathbf{n}\rangle$ with Hamiltonian \eqref{OriginalHamiltonian} is dual in the sense of \eqref{DualityRelation}, with respect to a process $|\bm{\xi}\rangle$ defined on the enlarged state space
\begin{equation}
    \widetilde{\Omega}:=\Omega\times \mathbb{N}_{0}^{V}
\end{equation}
with elements
\begin{equation}
    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|r_{1}^{x},\ldots,r_{N}^{x}\rangle\otimes |m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}\rangle\right)
\end{equation}
where $r_{x}^{k}$ denotes the number of dual particles of type $k\in \{1,\ldots,N\}$ at site $x\in V$ and $m_{k}^{\widetilde{x}}$ denotes the number of particles of species $k\in \{2,\ldots,N\}$ at an extra-site $\widetilde{x}$ connected to the site $x\in V$.\\
The Hamiltonian of the dual process reads as
\begin{equation}\label{DualHamiltonian}
    \widetilde{H}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{H}_{x}
\end{equation}

where $H_{x,y}$ is the one defined in \eqref{edgeHamiltonian}, while 
\begin{equation}\label{siteDualHamiltonian}
    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left((a^{\dagger})_{k}^{\widetilde{x}}\,E_{1k}^{x}-E_{kk}^{x}\right)
\end{equation}
By introducing the action of a bosonic creation operator $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, we define in \eqref{siteDualHamiltonian} 
$(a^{\dagger})_{k}^{\widetilde{x}}$ as a copy of $a^{\dagger}$ acting on the extra-site $\widetilde{x}$ and on the occupation of the species $k\in\{2,\ldots,N\}$. \\
The Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual with respect to the duality matrix $D$ defined as 
\begin{equation}
\label{duality-function-good}
    D=\bigotimes_{x\in V}\left(D_{x}\otimes D_{\widetilde{x}}\right)
\end{equation}
We denote by $D_{x}$ the site part. This is defined as 
\begin{equation}
    D_{x}=R_{x}\exp{(E^{x})}
\end{equation}
with 
\begin{equation}
    E^{x}=\sum_{k=2}^{N}E_{k1}^{x}
\end{equation}
that implies 
\begin{equation}
    \exp{(E^{x})}=I+E^{x}
\end{equation}
and where $R_{x}$ is the diagonal matrix with elements (up to a finite constant) the inverse of the masses of the reversible measure \eqref{reversibleMeasure}, i.e. 
\begin{equation}
    R_{x}=\sum_{n\in\chi}\frac{\prod_{k=1}^{N}n_{k}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
\end{equation}
where, for all $x\in V$, we call $\chi=\{(n_{k}^{x})_{k\in\{1,\ldots,N\}}\in \mathbb{N}_{0}\,:\, \sum_{k=1}^{N}n_{k}^{x}=\nu\}$ the simplex.\\ 
We denote by $D_{\widetilde{x}}$ the extra-site part. It is defined as
\begin{equation}\label{dualityMatrix}
D_{\widetilde{x}}=\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
\end{equation}
On one hand, the edge part of the dual Hamiltonian \eqref{DualHamiltonian} is a copy of \eqref{edgeHamiltonian}, therefore it performs the stirring dynamic on the graph. On the other hand, the site dual Hamiltonian \eqref{siteDualHamiltonian} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widetilde{x}$. This means that, eventually, only particles of type $1$ remain in the graph while all other types are absorbed by the extra-sites. Thinking about the type $1$ as the hole  the graph is eventually emptied, similarly to what proved in the SEP(2j)\cite{carinci2013duality}.
\subsection{Proof of the duality relation}\label{subsectionDualityProof}
To prove the duality relation between \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} with the duality matrix \eqref{duality-function-good} we shall show that 
\begin{equation}
    H^{T}D=D\widetilde{H}
\end{equation}
Since the duality matrix is a tensor product over the sites $x\in V$ it is enough to prove that for the edge Hamiltonians
\begin{equation}\label{edgeDualRealtion}
    H_{x,y}^{T}D=DH_{x,y}\qquad \forall x,y\in \mathcal{E}
\end{equation}
and for the site Hamiltonians 
\begin{equation}\label{siteDualRelation}
    H_{x}^{T}D=D\widetilde{H}_{x}\qquad \forall x\in V.
\end{equation}
We will prove these two statements seprately in the following.

@@

We fix arbitrary $m,m_{2},m_{3}\in \{0,\ldots,L\}$ such that $m=m_{2}+m_{3}$.  We replace the above eigenvectors in 
